Nanophotonic Computational Design

### 2013-03-03 paper/paper.tex
Finished solution method section draft.

\section{Method of solution}
We employed the alternating directions method of multipliers (ADMM) algorithm % Ref!
    in order to solve \eq{problem}.
ADMM, at its core, solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.

>>>>

\section{Method of solution}
We employed the alternating directions method of multipliers (ADMM) algorithm % Ref!
    in order to solve \eq{problem}.
The ADMM algorithm solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.

Since we are working in three dimensions, solving \eq{problem} for $x_i$ 
    is non-trivial in that it involves millions of variables and
    requires solving for the ill-conditioned $A_i(z)$ matrix.
For this reason, we use a home-built
    finite-difference frequency-domain (FDFD) solver which 
    implements a hardware-accelerated iterative solver % Ref!
    on Amazon's Elastic Compute Cloud.
Critically, our cloud-based solver allows us to scale to solve problems
    with arbitrarily-large number of modes,
    with no significant penalty in runtime.

In contrast to solving for $x_i$, solving for $z$ is much simpler since we
    only consider planar structures;
    thereby limiting $z$ to have only thousands of variables.

Lastly, in order to arrive at fully discrete, manufacturable structures,
    we convert $z$ to a boundary parameterization % Ref!
    and tune our structure using a steepest-descent method.
